---
title: "typistR: simple R interfaces to celltypist python library"
shorttitle: "interop with python for cell types"
author: "Vincent J. Carey, stvjc at channing.harvard.edu"
date: "`r format(Sys.time(), '%B %d, %Y')`"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{typistR: simple R interfaces to celltypist python library}
  %\VignetteEncoding{UTF-8}
output:
  BiocStyle::html_document:
    highlight: pygments
    number_sections: yes
    theme: united
    toc: yes
---

# Introduction

celltypist is a python library with model weights for 53 different
tissue or disease or developmental contexts for cell type classification
based on RNA-seq experiments.  The purpose of this package
is to demonstrate very lightweight interfacing to accomplish
tool reuse in R/Bioconductor.

# Setup and overview

Prior to adoption in Bioconductor,
install the package with devtools:
```{r doinst,eval=FALSE}
devtools::install_github("vjcitn/typistR")
```

An overview of available prediction contexts is:

```{r do1,message=FALSE}
library(typistR)
library(DT)
ctm = ct_models()
DT::datatable(ctm)
```

# Model objects

Here's an illustration of one of the available models.
basilisk and reticulate are used together.  
```{r ctmod}
lungat = model_desc(mname="Human_Lung_Atlas.pkl")
lungat
names(lungat)
```

Typically we want to convert all python values to R
values before returning from a basilisk call.  In this
case, we return the live python object because
it provides direct access to information about the
model in use.


